Social Visual Analytics: DevOps for Data Scientists

### 2015-03-20 conclusion.tex
fix

We presented a case for environments that support the visual
analytics process, from data acquisition and exploratory
data analysis, through development and deployment.
The environment supports collaboration and communication
through shared experimental workbooks with version control,
searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We implemented these ideas in the RCloud prototype.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work
benefit from having such capabilities.

This work prototype a step toward practical ``DevOps for data
science'' and offers reproducible experiments.
Possible next steps are to support cross-language development,
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

The code is available 
at \url{github.com/att/rcloud/}
under an MIT open source license.

>>>>

We presented a case for a data analytics environment that
supports the visual analytics process, from data acquisition
and exploratory data analysis, through development and deployment.
Building on the extensive previous work on requirements for
visual analytics systems, we designed and deployed a prototype
environment, RCloud.  RCloud supports collaboration and communication
through shared experimental workbooks with version
control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

Our purpose was to gain experience and insight by implementing and
deploying a prototype with a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support the broad visual analytics process.

Rcloud is a step toward practical ``DevOps for data science'' and
reproducible, publishable experiments.

Possible next steps are to support cross-language development,
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

RCloud code is available 
at \url{github.com/att/rcloud/}
under an MIT open source license.
